COVID19 - Forecast and predictions using a BYM model - Veneto Region

### 2020-03-17 BYM_model/INLA_def.Rmd
Add home page, navigation and theme

#import dataset shapefile Italian province

nc.province <- readOGR("BYM_model/ProvCM01012019_g",layer ="ProvCM01012019_g_WGS84")
nc.province<-nc.province[nc.province$COD_REG==Region,]
nc.province<-nc.province[order(nc.province$COD_PROV),]
nc.province$ID<-as.factor(nc.province$COD_PROV)
levels(nc.province$ID)<-1:length(levels(nc.province$ID))
nc.province$ID<-as.numeric(nc.province$ID)
#Create adjacency matrix
nc.nb <- poly2nb(nc.province,snap=0.01)
nb2INLA(paste(wd,"nc.adj",sep=""), nc.nb)
file.adj <- paste(wd,"nc.adj",sep="")
################################
```

>>>>

#import dataset shapefile Italian province
nc.province <- readShapePoly("../BYM_model/ProvCM01012019_g/ProvCM01012019_g_WGS84.shp")
nc.province<-nc.province[nc.province$COD_REG==Region,]
nc.province<-nc.province[order(nc.province$COD_PROV),]
nc.province$ID<-as.factor(nc.province$COD_PROV)
levels(nc.province$ID)<-1:length(levels(nc.province$ID))
nc.province$ID<-as.numeric(nc.province$ID)
#Create adjacency matrix
nc.nb <- poly2nb(nc.province,snap=0.01)
nb2INLA("nc.adj", nc.nb)
file.adj <- "nc.adj"
################################
```
